Offshore Indices of Abundance for <br/> Blue Crabs

### 2020-01-08 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
reorganized report

---0
title: "Offshore Indices of Abundance for <br/> Blue Crabs"
author: "Adam A Kemberling"
date: "1/4/2020"
output: 
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

@@

crabs %>% 
  mutate(STAT_ZONE = fct_rev(STAT_ZONE)) %>% 
  ggplot(aes(STAT_ZONE, Sapidus_Catch)) + 
  geom_boxplot(aes(group = STAT_ZONE)) + 
  labs(title    = "Blue Crab Catch by Stat Zone", 
       subtitle = "Stat zones ordered West to East - 2000 to 2018", 
       x        = "Statistical Zone",
       y        = "C. sapidus Single Station Catch") +
  facet_wrap(~Survey_design)

@@

>>>>

---
title: "Offshore Indices of Abundance for <br/> Blue Crabs"
author: "Adam A Kemberling"
date: "1/4/2020"
output: 
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

@@

@@

```{r}
crabs %>% 
  mutate(STAT_ZONE = fct_rev(STAT_ZONE)) %>% 
  ggplot(aes(STAT_ZONE, Sapidus_Catch)) + 
  geom_boxplot(aes(group = STAT_ZONE)) + 
  labs(title    = "Blue Crab Catch by Stat Zone", 
       subtitle = "Stat zones ordered West to East - 2000 to 2018", 
       x        = "Statistical Zone",
       y        = "C. sapidus Single Station Catch") +
  facet_wrap(~Survey_design)
```
